Sulfur Dioxide at Water's Surface

### 2010-12-23 EquilibratedResults.tex
so2 orientation

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/waterorientationsmall.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The top surface is located at a distance of 0 with negative positions in the bulk of the slab. The bottom slab surface is approx. 30\angs below the top surface. Shown are the angle distributions for $\theta$ (left column) and $\phi$ (right column) in both the neat-\wat~system (top row) and the saturated system (bottom row).}
		\label{fig:water-orientation}
	\end{center}
\end{figure}

@@

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/waterorientationsmall.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The top surface is located at a distance of 0 with negative positions in the bulk of the slab. The bottom slab surface is approx. 30\angs below the top surface. Shown are the angle distributions for $\theta$ (left column) and $\phi$ (right column) in both the neat-\wat~system (top row) and the saturated system (bottom row). Dark blue regions are void of water molecules above the top and below the bottom surfaces.}
		\label{fig:water-orientation}
	\end{center}
\end{figure}

@@

Orientation distributions of the adsorbed \suldiox~molecules were created for both the neat-\wat~and saturated \suldiox~systems. Figure \ref{fig:so2-orientation} shows the distributions of $\cos(\theta)$ and $\cos(\phi)$. As with the water orientation (figure \ref{fig:water-orientation}), the \suldiox~orients similarly in both of the surface equilibrated systems.

The location of \suldiox~within the water surface is slightly different between the two systems. The distribution of the single \suldiox~molecule is located just below the 0\angs position, and the distribution of the concentrated system is centered above the surface. This indicates that in both systems the \suldiox~is highly surface active, but the locations of the peak \suldiox~densities differ. The single molecule spends most of its time bound within the top water monolayer, and often traversing below that location by several\angs. The saturated system's surface molecules sit on top of the monolayer. The angular distribution of the single \suldiox~is concentrated primarily in $\cos(\theta)>0$ taking an orientation of the bisector pointing out of the water surface. This same distribution occurs in the saturated system for positions below 0\angs, but the orientation becomes isotropic for molecules located above 0\angs, on top of the water surface.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/so2orientationsmall.png}
		\caption{Molecular orientation distributions for \suldiox~molecules adsorbed to the water slab surface. Distributions are shown for $\cos(\theta)$ (left column) and $\cos(\phi)$ (right column) for both the neat-\wat~(top) and high \suldiox~concentration (bottom) systems. For both systems the $\theta$ distributions suggest \suldiox~bound to the water surface with the sulfur pointing towards the water slab, and the oxygens pointing to the gas phase. In this configuration the $\phi$ distribution is isotropic because of the water slab's in-plane symmetry.}
		\label{fig:so2-orientation}
	\end{center}
\end{figure}
